---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "33%"
)
library(analysistools)

```
# analysistools

This is a personal package gathering some functions I frequently use in analysis. Rather than searching for them, or remaking them time after time, I will be packaging them up here.

## Installation

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("suzanbaert/analysistools")
```
## Clustering functions

Get the kmeans elbow plot:

```{r kmeans_elbow}
kmeans_elbow(iris[-5])
```

Or get a second opinion on the number of clusters via Silhouette analysis. This shows the average silhouette width for each number of clusters.

```{r silhouette_plot}
silhouette_plot(iris[-5])
```



<br>
<hr>
<br>


## Plotting functions

+ `ggplot_colors(n)` gives the HEX codes of ggplot colors
